Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-11-11 paper/paper.tex
remove redundant info in appendix

To construct a dataset for exploring the perception of timbre, we conducted a survey on the perceived similarity of a set of sounds.
The set consists of $78$ recordings of different instrument--PT (IPT) pairs, each played at the same pitch (C4) and nuance \textit{mezzo forte}. For more information on the dataset considered in this study, see Section \ref{sec:subjective}.
In the survey, the subject is asked to organize dots on a two-dimensional place in a free sorting task.
Each dot corresponded to a different IPT recording and is moved by the user dragging them with the mouse.
In addition to spatially arranging the dots, the user is also asked to assign one of $20$ colors to each dot, providing a simple information of clustering of the sounds.
While both the location and color of each dot was recorded, only the color is used in our subsequent analysis---the spatial arrangement is only used to facilitate the user's ability to organize the sounds.
%More information on the data collection process is available in  Section \ref{sec:subjective}.

The above survey was implemented as an interactive website, links to which were sent out on internal mailing lists of the \emph{Conservatoire national sup\'erieur de musique et de danse de Paris} (CNSMDP) and international mailing lists focusing on research in audio and music processing.
We made the experiment available for two months, during which we obtained results for a total of $31$ subjects.
The final arrangement and color assignment of one of the subjects is shown in Figure \ref{fig:xp2display}.

@@

The subjects are thus asked to organize the 78 \ipts displayed as grey dots on a two dimensional plane into groups by assigning colors to each dots according to their "acoustic similarity". The textual instructions provided to introduce the experiment was chosen to be deliberately vague in order to allow the subject to follow its own judgment.

The plane is displayed on a computer screen using a web based interface\footnote{The interface is available here: http://soundthings.org/ticel/groupSounds}. The \ipts can be listened to by hovering the mouse on the corresponding dot. The experiment is over when the subject assigned a color to all the dots. The initial location of the dots on the plane is randomized for each subject and can be changed during the experiment by the subject for convenience. Event hough the location of the dots is recorded, this data is not considered during the analysis.

The experiment was available online for two months and requests to perform the test have been sent to internal mailing lists of the CNSMDP and international research mailing with a focus on audio and music processing. The experiment have been performed on a voluntary basis without gratification. Subjects were asked to use headphones at a comfortable listening level.

>>>>

In the survey, the subject is asked to organize dots on a two-dimensional place in a free sorting task.
Each dot corresponded to a different IPT recording and is moved by the user dragging them with the mouse.
In addition to spatially arranging the dots, the user is also asked to assign one of $20$ colors to each dot, providing a simple information of clustering of the sounds.
While both the location and color of each dot was recorded, only the color is used in our subsequent analysis---the spatial arrangement is only used to facilitate the user's ability to organize the sounds.
%More information on the data collection process is available in  Section \ref{sec:subjective}.

The final arrangement and color assignment of one of the subjects is shown in Figure \ref{fig:xp2display}.

@@
